COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-11-18 main.tex
Update reference to our paper

Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2018arXiv181007201W}). This amplitude can be thought of as the 'width' over which the perturbations of the resonance are effective. Variations in eccentricity follow the semi-major axis variations according to the Tisserand relation

@@

To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of the collision module implementation can be found in \citet{2018arXiv181007201W}.

>>>>

Under the effect of MMR, a body will undergo oscillations in semi-major axis and eccentricity. So long as the gravitational force on the body is dominated by the central star and the perturbing body, the amplitude of the oscillations in semi-major axis can be described using the pendulum approximation (see equation 6 in \citet{2019MNRAS.489.2159W}). This amplitude can be thought of as the 'width' over which the perturbations of the resonance are effective. Variations in eccentricity follow the semi-major axis variations according to the Tisserand relation

@@

To follow the dynamical and collisional evolution of a planetesimal disk, we use the highly parallel N-body code {\sc ChaNGa} \footnote{A public version of {\sc ChaNGa} can be downloaded from \url{http://www-hpcc.astro.washington.edu/tools/ChaNGa.html}}. This code, which is written in the {\sc CHARM++} parallel programming language, was originally designed for cosmology simulations and has been shown to perform well on up to half a million processors \citep{2015AphCom..2..1}. {\sc ChaNGa} calculates gravitational forces using a modified Barnes-Hut \citep{1986Natur.324..446B} tree with hexadecapole expansions of the moments. All of the simulations we perform use a node opening criterion of $\theta_{BH}$ = 0.7. More information about the code can be found in \citet{2008IEEEpds...ChaNGa}. We have also recently modified {\sc ChaNGa} to handle solid-body collisions. A full description of the collision module implementation can be found in \citet{2019MNRAS.489.2159W}.
